Fixing Vulnerabilities Hinders Maintainability

### 2019-02-07 paper/ICPC19/icpc19.tex
fixes

Every SSL/TLS connection, \texttt{s}, begins with a handshake which is responsible by the
negotiation between two parties. DTLS provides a mechanism for fragmenting a
handshake message over a number of packets, each of which can be transmitted
separately over the Internet from one party to another. The problem in CVE-$2014$-$3506$ 
is that the size of the handshake message collected by the receiver is not verified against 
the maximum size allowed by DTLS and latter in the code it is allocated to a new fragment (line $37$). 
Thus, if an attacker has access to one of these packages it can change the handshake messsage size and
trigger unnecessary memory allocations of large length which can lead to memory exhaustion that could
could end in a DoS attack.

>>>>

Every SSL/TLS connection, \texttt{s}, begins with a handshake which is responsible by the
negotiation between the two parties. DTLS provides a mechanism for fragmenting a
handshake message over a number of packets, each of which can be transmitted
separately over the internet from one party to another. The problem in CVE-$2014$-$3506$ 
is that the size of the handshake message collected by the receiver is not verified against 
the maximum size allowed by DTLS. It is then allocated to a new fragment (line $37$). 
Thus, if an attacker has access to one of these packages, the attacker can change the handshake messsage size and
trigger unnecessary memory allocations of large length which can lead to memory exhaustion that could
could end in a DoS attack.
